\documentclass[12pt,a4paper]{article}

\usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[binding=5mm]{layaureo}         % margini ottimizzati per l'A4; rilegatura di 5 mm
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx,floatflt}
\usepackage{xcolor}
\usepackage{color}
\usepackage{tikz}
\usepackage[margin=1.5cm]{geometry}
\usepackage{tabto}
\usepackage{xcolor}
\usepackage[colorlinks=true, linkcolor=blue,urlcolor=blue]{hyperref}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\@title}

  \@author
\end{flushleft}\egroup
}
\makeatother




\date{}

\begin{document}
%\maketitle
{ \setlength{\parindent}{0cm}
\begin{small}
\begin{flushleft}
\begin{minipage}{0.6\textwidth}
\textbf{Paolo \textsc{Sabatini}}\newline
{\footnotesize
\textsc{Address}: \tabto*{2cm} 40, Via T. Sabatini\\
\tabto*{2cm} 53021, Abbadia San Salvatore (IT)\\
\textsc{Mobile}:\tabto*{2cm} +393385968853\\
\textsc{EMail}:\tabto*{2cm} paolosbtn@gmail.com
}
\end{minipage}
\end{flushleft}

\vspace{2cm}

Dear \texttt{\color{red!80!black}INSERT NAME},

I'm writing this cover letter to apply to the position for \texttt{\color{red!80!black}INSERT POSITION}.
Your position, in a high profile environment, looks very interesting to me and I feel to fit perfectly for this role. My entire education so far has been focused on science, starting from a scientific high school to my MSc and current PhD in high energy physics, leading to very competitive and high standard working  
experience. \\[2mm]

Leaving abroad since 2016 made me very confident in an international community, improving my communication and networking skills. Moreover working at the European Nuclear Research Center (CERN) gave me the opportunity to work in many different topics, connecting different groups heading to mutual projects. Being a high energy physicist working at hadronic colliders in data analysis brings you to aim for the best performance of your research, and in my case, coding the best codes in terms of performance, user friendliness, trying to investigate at most on all the small bugs and optimisation chances. Of course this aims to a final physics measurement, performed by using the most modern data analysis techniques. In the meantime being involved in hardware projects, e.g. the monitoring of one of the most important sub-detector of the ATLAS experiment, gave me the measure of the implementation and complexity of hardware data acquisition systems.\\[2mm]

My experience in coding and collaborating with groups can bring a new approach to problems, not from an engineering point of view, but from a high profile researcher who has experienced many straight on the edge techniques. The need I had in problem-solving, led me to have no difficulties in learning from the scratch and challenge myself every time with new goals. The motivation that only a ultra-competitive group such as yours can give is my bread for perform at best and stimulate the other components of the group.\par

I would like to ask you to consider my application for \texttt{\color{red!80!black}INSERT POSITION} and give me the chance to test you my motivation and skills in a dedicated interview.\\[2mm]

Sincerely,\\[0.5mm]
\tabto{0.5cm} Paolo Sabatini


\end{small}


}
\end{document}
